Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-14 Paper/ms.tex
v, acknowledgements

Consider a test particle moving in the $x$-$y$ plane under the influence of a
point mass at the origin. The equations of motion for the particle are:
\begin{eqnarray}
\frac{d^2x}{dt^2} &=& -\frac{x}{r^3} \\
\frac{d^2y}{dt^2} &=& -\frac{y}{r^3} \\
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$. The initial conditions
$\{x(0), y(0), \dot{x}(0), \dot{y}(0)\} = \{1, 0, 0, v\}$.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
BJB is partially
supported by the Marsden Fund (Royal Society of New Zealand).

>>>>

Consider a test particle moving in the $x$-$y$ plane under the influence of a
point mass at the origin. The equations of motion for the particle are:
\begin{eqnarray}
\frac{d^2x}{dt^2} &=& -\frac{x}{r^3} \\
\frac{d^2y}{dt^2} &=& -\frac{y}{r^3} \\
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$. The ODEs can be solved for any given set of
initial conditions for $x$, $y$, $\frac{dx}{dt}$, and $\frac{dy}{dt}$ to yield
the shape of the orbit. To simulate orbits
of different ellipticities, we set the initial position to $(1, 0)$, and
the initial velocity to $(0, v)$ where $v \in [0.4, 1]$.
If $v=1$, the orbit is circular and as $v$ decreases the orbit becomes more
elliptical.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Fengji Hou and David Hogg (NYU) for inspiring me to
finally work on this problem, and Phil Gregory (UBC) for writing so many
interesting papers on it. This work was supported by a Marsden Fast Start
grant from the Royal Society of
New Zealand.
